\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
component

The results of the experiment are shown in Table \ref{table:results}. Seven sets of graphs were tested for isomorphisms, and three cases the computation times are significantly different. In the other cases, the difference in computation time is not obviously related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times. This is most likely due to the circumstances of both executions of the algorithms did not occur under the exact same circumstances, as it was impossible to ensure the conditions were the same.

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 5.0530 sec & 5.4318 sec & 0.0207 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each graph, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}

>>>>

The results of the experiment are shown in Table \ref{table:results}. Seven sets of graphs were tested for isomorphisms, and three cases the computation times are significantly different. In the other cases, the preprocessing time is relatively very small. This is because the low complexity of \emph{gettwins} and the fact that \emph{preprocessing} does nothing when there are no (false) twins. The difference in computation time is not obviously related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times. This is most likely due to the circumstances of both executions of the algorithms did not occur under the exact same circumstances, as it was impossible to ensure the conditions were the same.

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 5.0530 sec & 5.4318 sec & 0.0207 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}
